%%%%%%%% M.Sc. Disseratation Template%%%%%%%%%%%
%%%%%%%% SMIT_LaTeX Workshop August 2019%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt, a4paper]{report}
\pagestyle{headings} % other package fancyhdr, to get running heads on the top
\usepackage{amsthm,amssymb,amsmath,mathrsfs}
\usepackage{bold-extra,epsfig,pst-all}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{lineno}

\usepackage{cite}
\renewcommand{\bibname}{References}
% Uncomment the following line for screen version
% \usepackage[dvips,bookmarks,bookmarksopen=false,colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref} % hyperlinks in pdf doc
%-------------------------PAGE SETTINGS ------------------------
\setlength{\textheight}{210mm}%%%Best 210
\setlength{\textwidth}{140mm}%Best140
\setlength{\headheight}{14pt}
\oddsidemargin=2cm
\evensidemargin=2cm 
\topmargin 0.15in
\headheight 15pt
\parindent .5cm
\interfootnotelinepenalty=1000


%------------------------- Definitions ------------------------------       
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\newtheorem{conjecture}{Conjecture}[chapter]
\newtheorem{example}{Example}[chapter]
\newtheorem{problem}{Problem}[chapter]
\newtheorem{remark}{Remark}[chapter]
\newtheorem{definition}{Definition}[chapter]

\newtheoremstyle{fordefn}% name
     {}%  Space above
     {}%  Space below
     {\rm}%  Body font
     {}%  Indent amount (empty = no indent, \parindent = para indent)
     {\bf}%  Thm head font
     {.}%  Punctuation after thm head
     {.5em}%  Space after thm head: " " = normal interword space; \newline = linebreak
     {\thmname{#1}\thmnumber{ #2}\thmnote{ [#3]}}%   Thm head spec (can be left empty, meaning `normal')
\theoremstyle{fordefn}

\newenvironment{preface}[1]{
 \newpage \thispagestyle{empty}
%   \addcontentsline{toc}{chapter}{#1}
  \begin{center}\vspace*{1.5cm} {\Large \bfseries #1} \vspace{0.5cm}\end{center}
}{}

\newcommand{\thesistitle}{\baselineskip=22pt {On Canonical Consistency of 2-path Signed Graphs}}
\newcommand{\authorname}{\baselineskip=22pt {ANJAN GAUTAM}}
\newcommand{\tao}{{\Large $\tau$}}
\newcommand{\taom}{{\Large $\tau_m$}}
\newcommand{\taos}{{\Large $\tau_3$}}
\newcommand{\la}{\xleftarrow}
\newcommand{\thla}{\twoheadleftarrow}
\newcommand{\ra}{\xrightarrow}
\newcommand{\girth}[1]{\mathit{g}(#1)}
\newcommand{\eoe}{{\hfill $\triangle$\\}}
%%%%%%%%%%%Page Numbering%%%%%%%%%%%%%%%%%%%%%%%%%
\pagenumbering{roman}

% %------------------------- document ---------------------------------
\begin{document}
\linenumbers
% \pagenumbering{roman}  %-------page number for initial pages----------
% % \fancypagestyle{plain}{
% % \fancyhf{}
% % \fancyfoot[C]{}
% % \fancyfoot[C]{{\sf{--~\thepage~--}}} 
% % \renewcommand{\headheight}{0pt}
% % \renewcommand{\headrulewidth}{0.0pt}
% % % \renewcommand{\footrulewidth}{0.5pt}
% % }
% %--------------------------------------------------------
\pagestyle{fancy}
\thispagestyle{empty}
\lhead{\nouppercase{\rightmark}}
\renewcommand{\headrulewidth}{0pt}
\setcounter{page}{2}
\input{frontmatter}
\renewcommand{\headrulewidth}{0.5pt}
\fancyhead[L]{}\pagenumbering{arabic}
\fancyhead[R]{}
\fancyhead[L]{\sffamily\rightmark}
\lhead{\nouppercase{\rightmark}}
\tableofcontents
\input{symbols}
\addcontentsline{toc}{chapter}{List of Symbols}
\listoffigures 
\addcontentsline{toc}{chapter}{List of Figures}
% \newpage
% %-------------------setting page number--------------------------
% \pagenumbering{arabic}
% \pagestyle{fancy}
\baselineskip=22pt %---------line spacing-----------------------
% \setcounter{chapter}{0}
% \setcounter{page}{1} 
% %---------------Comment------------------------------
% \newcommand{\comment}[1]{\marginpar{\footnotesize #1}}
% % \newcommand{\comment}[1]{}
% \newcommand{\commentbd}[1]{\marginpar{\footnotesize \red #1}}
% % \newcommand{\commentbd}[1]{}
% %--------heading customize-------------------
% \fancyhead[L]{}
% \fancyhead[R]{}
% \fancyhead[L]{\sffamily\rightmark}
% %--------------page style for the first page of a chapter-----------------
% \fancypagestyle{plain}{
% \fancyhf{}
% \fancyfoot[C]{}
% \fancyfoot[C]{{\sf{--~\thepage~--}}} 
% \renewcommand{\headheight}{0pt}
% \renewcommand{\headrulewidth}{0.0pt}
% % \renewcommand{\footrulewidth}{0.5pt}
% }
% %------------to get uniform page number style in every pa\setcounter{page}{3}ge----------
% \fancyfoot[C]{}
% \fancyfoot[C]{{\sf{--~\thepage~--}}} 
% \lhead{\nouppercase{\rightmark}}

%%%%%%%%% Contents of The Thesis %%%%%%%%%%%%%%
% \input{response}
\input{chapter1}   % Introduction
% \pagenumbering{arabic}
\input{chapter2}   % 
\input{chapter3}   % Non-negative Matrices

%  \input{rough24}
%------------------ Bibliography---------------------------
% \section{References}
\addcontentsline{toc}{section}{\bf References}
\bibliographystyle{plain}
\begin{thebibliography}{10}
% \bibliography{kshittiz}
\bibitem{ACH83}
B.~Devdas Acharya.
\newblock A characterization of consistent marked graph.
\newblock {\em National Academy Science Letters.}, 6:431--440, 1983.

\bibitem{ACH84}
B.~Devdas Acharya.
\newblock Some further properties of consistent marked graphs.
\newblock {\em Indian Journal of Pure and Applied Mathematics}, 15(8):837 --
  842, 1984.

\bibitem{BEI78}
Lowell~W. Beineke and Frank Harary.
\newblock Consistency in marked digraphs.
\newblock {\em Journal of Mathematical Psychology}, 18:260--269, 1978.

\bibitem{BEI1978}
Lowell~W. Beineke and Frank Harary.
\newblock Consistent graphs with signed points.
\newblock {\em Rivista di matematica per le scienze economiche e sociali},
  1(2):81--88, Sep 1978.
  
\bibitem{SIN13}
Deepa Sinha and Pravin Garg.
\newblock A characterization of canonically consistent total signed graphs.
\newblock {\em Notes on Number Theory and Discrete Mathematics.}, 19(3):70 --
  77, 2013.

\bibitem{BON15}
Miklos Bona.
\newblock {\em Handbook of Enumerative Combinatorics.}
\newblock CRC Press, 2015.

\bibitem{HAR56}
D.~Cartwright and F.~Harary.
\newblock Structural balance: a generalization of heider's theory.
\newblock {\em Psychological Review.}, 63(5):277 -- 293, 1956.


\bibitem{HAR53}
Frank Harary.
\newblock On the notion of balance of a signed graph.
\newblock {\em Michigan Math. J.}, 2(2):143--146, 1953.

\bibitem{har69}
Frank Harary.
\newblock {\em {Graph Theory}}.
\newblock Addison-Wesley, Reading, MA, 1969.

\bibitem{KAB80}
Frank Harary and Jerald~A. Kabell.
\newblock A simple algorithm to detect balance in signed graphs.
\newblock {\em Mathematical Social Sciences}, 1(1):131 -- 136, 1980.

\bibitem{HARA81}
Frank Harary and Jerald~A. Kabell.
\newblock Counting balanced signed graphs using marked graphs.
\newblock {\em Proceedings of the Edinburgh Mathematical Society},
  24(2):99–104, 1981.

\bibitem{HOE92}
Cornelis Hoede.
\newblock A characterization of consistent marked graphs.
\newblock {\em Journal of Graph Theory}, 16(1):17--23, 1992.

\bibitem{DEN50}
Denes Konig.
\newblock {\em Theorie der endlichen und unendlichen graphen.}
\newblock Chelsea Publishing Company, 1950.

\bibitem{RAO84}
S.B Rao.
\newblock Characterization of harmonious marked graphs and consistent nets.
\newblock {\em Journal of combinatorics, information and system sciences.},
  9:97 -- 112, 1984.

\bibitem{ROB95}
Fred~S. Roberts.
\newblock On the problem of consistent marking of a graph.
\newblock {\em Linear Algebra and its Applications}, 217:255 -- 263, 1995.
\newblock Proceedings of a Conference on Graphs and Matrices in Honor of John
  Maybee.

\bibitem{ROB03}
Fred~S Roberts and Shaoji Xu.
\newblock Characterizations of consistent marked graphs.
\newblock {\em Discrete Applied Mathematics}, 127(2):357 -- 371, 2003.
\newblock Ordinal and Symbolic Data Analysis (OSDA '98), Univ. of
  Massachusetts, Amherst, Sept. 28-30, 1998.

\bibitem{SIN11}
Deepa Sinha and Pravin Garg.
\newblock Balance and consistency of total signed graphs.
\newblock {\em Indian Journal of Mathematics.}, 53(1):71-- 81, 2011.

\bibitem{SINHA11}
Deepa Sinha and Pravin Garg.
\newblock Characterization of total signed graph and semi-total signed graphs.
\newblock {\em International Journal of Contemporary Mathematical Sciences.},
  6(5):221-- 228, 2011.
  
\bibitem{REDDY09}
P. S. K Reddy and M S Subramanya.
\newblock Note on path signed graphs.
\newblock {\em Notes on Number Theory and Discrete Mathematics.},
  4(16), 2009.
  
\bibitem{SIN17}
Deepa Sinha and Deepakshi Sharma.
\newblock Characterization of 2-Path Product Signed Graphs with
Its Properties.
\newblock {\em Computational Intelligence and Neuroscience},
  2017.


\end{thebibliography}
\end{document}

